A radiocarbon data based evaluation of Cultural Transmission in Bronze Age burial rites of Central, Northern and North-western Europe

### 2018-12-17 article/03_Results.Rmd
improvements of "England"

`r a("England")`:
The *England* region stretches across England to the heights of York and Liverpool, incorporating parts of Wales and leaving out Cornwall and Devon in the southwest. In fact, it also touches a narrow coastal strip on the mainland, from which no ^14^C data are available. The available data are concentrated in the southeast of Britain, but are well distributed there. The diachronic data availability is relatively good in the early and middle Bronze Age, but then decreases in the late Bronze Age. *burial type* and *burial construction* behave accordingly. The relative development derived from the ^14^C data indicates the correct trend for *burial type*: Cremation graves became more and more important during the Bronze Age, while body burials were practiced for a long time in parallel. However, the data set emphasizes the dominance of the cremation graves too much. With regard to the variables *burial construction*, the basic dominance of burial mounds corresponds perfectly to the archaeological narrative, but nevertheless -- especially in the Late Bronze Age -- flat grave fields also occurred, which the data set wrongly excludes.

>>>>

`r a("England")`:
The *England* region stretches across England up to York and Liverpool, incorporating parts of Wales and leaving out Cornwall and Devon in the southwest. It also touches a narrow coastal strip on the mainland, from which no ^14^C data are documented. The available data are concentrated in the southeast of Britain, but are well distributed there. The diachronic data availability is relatively good in the early and middle Bronze Age, but then decreases in the late Bronze Age. *burial type* and *burial construction* behave accordingly. The relative development derived from the ^14^C data indicates the correct trend for *burial type*: Cremation graves became more and more important during the Bronze Age, while inhumations were practiced for a long time in parallel. However, the data set emphasizes the dominance of the cremation graves too much. With regard to the variables *burial construction*, the basic dominance of burial mounds corresponds perfectly to the archaeological narrative, but nevertheless -- especially in the Late Bronze Age -- flat grave fields also occurred, which the data set wrongly excludes.
